Measuring neutron star tidal deformability with Advanced LIGO: a Bayesian analysis of mixed binary observations

### 2016-05-25 Paper/paper.tex
text on second part

\red{
Somewhat reduce discussion of results. Discuss in order of probability, starting
with low SNR, ending with exceptional events.
}
\prayush{
Next, we study the ability of aLIGO to constrain neutron star tidal 
deformability with a single observation of coalescing NSBHs. For this, we
use the same setup and parameter choices for signal waveforms as before, but
replace the template model with one that includes tidal effects from inspiral
through to merger~\cite{Lackey:2013axa} (i.e. LEA+). First of all, this reduces
the biases in the measurement of non-tidal parameters. Second, as we can see
from Fig.~\ref{fig:TT_LambdaCIWidths90_0_Lambda_SNR}, at signal-to-noise
ratios $\simeq 20-30$, only under the most favorable circumstance (including a
BH with mass within the ``mass-gap'') can we put a factor of $1.5-2$ bound on
$\lambdans$ at $90\%$ confidence level. For similar signals with 
$\rho\gtrsim 30$ we can constrain $\lambdans$ within $\pm 50\%$ of its true
value. For more realistic SNRs and BH parameters, a single measurement is 
for $\lambdans$ is accompanied with a $\sim\pm150+\%$. uncertainty.
% While these
% results are expected, multiple realistic observations is the next window that 
% we explore in order to obtain more information on $\lambdans$. These results 
% are detailed in Sec.~\ref{s1:PEwithNS}.
}

@@

>>>>

% \red{
% Somewhat reduce discussion of results. Discuss in order of probability, starting
% with low SNR, ending with exceptional events.
% }

% \prayush{
Second, we study the ability of aLIGO to constrain neutron star tidal 
deformability with a single observation of NSBH merger. For this, we
use the same setup for signal waveforms as before, but replace the filter
template model with one that includes tidal effects from inspiral
through to merger (i.e. LEA+)~\cite{Lackey:2013axa}. For most binaries with
BH masses outside of the mass-gap and/or realistic signal-to-noise
ratios (SNR), we find it difficult to put better than a factor of $2$ bound
on $\lambdans$ with a single observation. As we can see from
Fig.~\ref{fig:TT_LambdaCIWidths90_0_Lambda_SNR}, it is only at SNRs 
$\rho\gtrsim 20-30$ (under otherwise favorable circumstances) that we are able
to bring this down to a $\pm 75\%$ bound on $\lambdans$. For signals louder
than $\rho =30$, we can constrain $\lambdans$ to a much more meaningful degree
(within $\pm 50\%$ of its true value).
% For more realistic SNRs and BH parameters, a single measurement is 
% for $\lambdans$ is accompanied with a $\sim\pm150+\%$. uncertainty.
% }
While this is discouraging at first, we turn to ask: what if we combine
information from a population of low-SNR observations?

@@

% \prayush{
